%
% ---- Bibliography ----
%
\bibliographystyle{spmpsci}
\begin{thebibliography}{}


% \bibitem {czaj}
% Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid information services
% for distributed resource sharing. In: Proceedings 10th IEEE International Symposium
% on High Performance Distributed Computing, pp. 181--184. IEEE, New York (2001).
% \doi{10.1109/HPDC.2001.945188}


\bibitem {m1}
Voevodin, V., Voevodin, Vl.:
Parallel Computing.
BHV-Petersburg, St. Petersburg. 608~p. (2002)
%\url{https://www.studmed.ru/voevodin-vv-parallelnye-vychisleniya\_42cf5ce8568.html}
\bibitem {m2}
Antonov, A., Volkov, N.:
Study of the Algorithms Information Structure as the Basis of a Training Workshop.
Communications in Computer and Information Science, vol.~1510, pp.~404--414 (2021).
\doi{10.1007/978-3-030-92864-3\_31}
\bibitem {m3}
Antonov, A., Frolov, A., Kobayashi, H., Konshin, I., Teplov, A., Voevodin, Vad., Voevodin, Vl.:
Parallel Processing Model for Cholesky Decomposition Algorithm in AlgoWiki Project.
Supercomputing Frontiers and Innovations, vol.~3, no.~3, pp.~61--70 (2016).
\doi{10.14529/jsfi160307}
\bibitem {m4}
Open Encyclopedia of Parallel Algorithmic Features.
\url{http://algowiki-project.org}
\bibitem {a1}
Voevodin, V., Antonov, A., Dongarra, J.:
AlgoWiki: an Open Encyclopedia of Parallel Algorithmic Features.
Supercomputing Frontiers and Innovations, Vol.~2, N.~1. Pp.~4--18 (2015).
\doi{10.14529/jsfi0101}
%\bibitem {m5}
%AlgoWiki. Algorithm graph visualization standard.
%\url{https://algowiki-project.org}
\bibitem {m6}
Koch, P.-P.:
The Document Object Model: an Introduction. \url{https://www.digital-web.com/articles/the\_document\_object\_model/}
\bibitem {m7}
Brownell, D.:
SAX2. Gravenstein Highway North, Sebastopol: O’Reilly Media, 240~p. (2002)
% \bibitem {m8}
% Difference between DOM vs SAX Parser in Java --- XML Parsing in Java. \url{https://www.java67.com/2012/09/dom-vs-sax-parser-in-java-xml-parsing.html\#ixzz7xtkySKLe}
\bibitem {m9}
Sukumar, P.:
How to Parse XML in C++. \url{https://linuxhint.com/parse\_xml\_in\_cpp/}
\bibitem {m10}
RapidXML library documentation. \url{https://rapidxml.sourceforge.net/}
\bibitem {m11}
PugiXML library documentation. \url{https://pugixml.org/}
\bibitem {m12}
TinyXML library documentation. \url{https://github.com/leethomason/tinyxml2}
% \bibitem {m13}
% PugiXML. Benchmarks. \url{https://pugixml.org/benchmark.html}
\bibitem {m14}
XSD: XML Data Binding for C++. \url{https://www.codesynthesis.com/products/xsd/}
\bibitem {m15}
Documentation of the RapidJSON library. \url{http://rapidjson.org/}
% \bibitem {m16}
% ExprTk library documentation. \url{https://github.com/ArashPartow/exprtk}
\bibitem {m17}
C++ Mathematical Expression Parsing And Evaluation Library. \url{http://www.partow.net/programming/exprtk/}
% \bibitem {m18}
% Joel Jones. Abstract Syntax Tree Implementation Idioms. \url{https://hillside.net/plop/plop2003/Papers/Jones-ImplementingASTs.pdf}
\bibitem {m19}
Documentation of the muParser library series. \url{https://beltoforion.de/en/muparserx/}
% \bibitem {m20}
% Muparser library documentation. \url{https://beltoforion.de/en/muparser/}
% \bibitem {m21}
% METL library documentation. \url{https://github.com/TillHeinzel/METL}
\bibitem {m22}
C++ Mathematical Expression Parser Benchmark. \url{https://github.com/ArashPartow/math-parser-benchmark-project}
\bibitem {m23}
Chaomei, S.:
Graph Drawing Algorithms (2006).
\doi{10.1007/1-84628-579-8\_3}
%\url{https://www.researchgate.net/publication/319727107\_Graph\_Drawing\_Algorithms}
\bibitem {m24}
Sim, S.:
Automatic Graph Drawing Algorithms (1999). \url{https://www.researchgate.net/publication/2271614\_Automatic\_Graph\_Drawing\_Algorithms}
\bibitem {m25}
Gansner, E.R., Koutsofios, E., North, S.C., Vo, K.-P.:
A technique for drawing directed graphs. IEEE Transactions on Software Engineering, vol.~19, no.~3, pp.~214--230 (1993). \doi{10.1109/32.221135}
%\url{https://ieeexplore.ieee.org/document/221135}
\bibitem {m26}
Kasyanov, V.N.:
Methods and Tools for Visualization of Graphs and Graph Algorithms. International Journal of Applied Mathematics and Informatics, 15, pp.~78--84 (2021). \doi{10.46300/91014.2021.15.13}
%\url{https://www.naun.org/main/UPress/ami/2021/a262013-013(2021).pdf}
\bibitem {m27}
Burch, M., Wallner, G., Wetering, H., Rooks, F., Morra, O.:
Visual Analysis of Graph Algorithm Dynamics. 14th International Symposium on Visual Information Communication and Interaction (2021). \doi{10.1145/3481549.3481550}
%\url{https://dl.acm.org/doi/10.1145/3481549.3481550}
\bibitem {m28}
Official website of the OpenGL library. \url{https://www.opengl.org}
\bibitem {m29}
Official website of the WebGL library. \url{https://www.khronos.org/webgl}
\bibitem {m30}
Carson, D.:
WebGL: Graphics and Animation (2020).
\doi{10.13140/RG.2.2.18538.95683}
%\url{https://www.researchgate.net/publication/344244517\_Research-Paper-WebGL}
\bibitem {m31}
Bian, M.J., Gao, H.H., Gao, J., Xu, J.P.:
Research and Application of Web3D Exhibition Based on WebGL and Html5. International Conference on Electrical, Automation and Mechanical Engineering (2015).
\doi{10.2991/eame-15.2015.220}
%\url{https://www.researchgate.net/publication/300618815\_Research\_and\_Application\_of\_Web3D\_Exhibition\_Based\_on\_WebGL\_and\_Html5}
\bibitem {m32}
Official website of the Three.js library. \url{https://threejs.org}
\bibitem {m33}
Danchilla, B.:
Three.js Framework. In book: Beginning WebGL for HTML5, pp.~173--203 (2012).
\doi{10.1007/978-1-4302-3997-0\_7}
%\url{https://www.researchgate.net/publication/302306483\_Threejs\_Framework}
\bibitem {m34}
Official website of the Babylon.js library. \url{https://www.babylonjs.com}
\bibitem {m35}
Official website of the VTK (Visualization Toolkit) library. \url{https://vtk.org}
\bibitem {m36}
Official website of the OpenSceneGraph library. \url{http://www.openscenegraph.com}
\bibitem {m37}
Official website of the DirectX API. \url{https://www.microsoft.com/ru-ru/download/details.aspx?id=35}
\bibitem {m38}
Official website of the Unity library. \url{https://unity.com}
\bibitem {m39}
Official website of the Blender platform. \url{https://www.blender.org}
\bibitem {m40} 
Official website of the Maya platform. \url{https://www.autodesk.com/products/maya/overview}
\bibitem {m41}
AlgoWiki. Glossary. \url{https://algowiki-project.org/en/Glossary}
% \bibitem {m42}
% David Flanagan. JavaScript Pocket Reference, 3rd Edition. \url{https://www.oreilly.com/library/view/javascript-pocket-reference/9781449335977}
\bibitem {m43}
Official documentation of the OrbitControls module. \url{https://threejs.org/docs/\#examples/en/controls/OrbitControls}
\bibitem {m44}
GitHub repository of the dat.GUI module. \url{https://github.com/dataarts/dat.gui}
\bibitem {m45}
Majeed, A., Rauf, I.:
MVC Architecture: A Detailed Insight to the Modern Web Applications Development (2018).
\url{https://crimsonpublishers.com/prsp/pdf/PRSP.000505.pdf}
\bibitem {m46}
Pop. D.-P., Samuel, A.:
Designing an MVC Model for Rapid Web Application Development. Procedia Engineering, 69 (2014).
\doi{10.1016/j.proeng.2014.03.106}
%\url{https://www.researchgate.net/publication/275540078\_Designing\_an\_MVC\_Model\_for\_Rapid\_Web\_Application\_Development}
\bibitem{vvv_lom2}
Voevodin, V., Antonov, A., Nikitenko, D., Shvets, P., Sobolev, S., Sidorov, I., Stefanov, K., Voevodin, V., and Zhumatiy, S.:
Supercomputer Lomonosov-2: Large Scale, Deep Monitoring and Fine Analytics for the User Community.
Supercomputing Frontiers and Innovations \textbf{6} {2}, 4--11 (2019).
\doi{10.14529/jsfi190201}



% \bibitem {m47}
% The official website of the Flask web framework. \url{https://flask.palletsprojects.com/en/3.0.x/\#}
% \bibitem {m48}
% Official website of the Docker platform. \url{https://www.docker.com/why-docker}
% \bibitem {m49}
% P. Gajer, M. Goodrich, S. Kobourov, A Fast Multi-Dimensional Algorithm for Drawing Large Graphs, 2000. \url{https://www2.cs.arizona.edu/~kobourov/grip\_paper.pdf}
% \bibitem {m50}
% M.Dodo, F.Andriamanampisoa, P.Torguet, J.Jessel, A new method to optimize the force-directed placement for 3D large graph drawing, 2007. Conference: Proceedings of the 5th International Conference on Computer Graphics, Virtual Reality, Visualization and Interaction. \doi{10.1145/1294685.1294709}. \url{https://www.researchgate.net/publication/220804553\_A\_new\_method\_to\_optimize\_the\_force-directed\_placement\_for\_3D\_large\_graph\_drawing}
% \bibitem {m51}
% GitHub repository for the MeshLine algorithm. \url{https://github.com/spite/THREE.MeshLine}
% \bibitem {m52}
% GitHub repository for the TextSprite algorithm. \url{https://github.com/SeregPie/THREE.TextSprite}
% \bibitem {m53}
% GitHub repository for the TextTexture algorithm. \url{https://github.com/SeregPie/THREE.TextTexture}

\end{thebibliography}
